Distortion corrected kernel density estimate on Riemannian manifolds

### 2022-10-30 paper/paper.tex
Fix Figure 9 where top 67 anomalies have the same rank 33.5 and appear in a horizontal line
This is because the true densities are all below 1e-7

Following similar steps to \autoref{twodgaussian}, we estimate the densities of the 4-D manifold and compare them with the ground truth density in \autoref{fig:fivedisomapden}. The bandwidth parameter for the DC-KDE estimator is set as \(r=1\) for this example. In \autoref{fig:fivedisomapden}, the log-scale ranks of the estimated density from distortion corrected KDE shown in the left panel and KDE shown in the right panel are compared with the true rank of density for four manifold learning embeddings, ISOMAP, LLE, Laplacian Eigenmaps and UMAP. Note that we exclude t-SNE algorithm in this section because it is designed mainly for low-dimensional visualization purposes and is only applicable to embedding dimensions within three.
Similar to \autoref{fig:fivedmeta}, the point shapes indicate the Gaussian mixture components and the colors indicate the distance to the kernel cores with outliers shown in darker colors. The grey shading area highlights the \(>99\%\) highest density region area and points falling into this area are the correctly classified top \(1\%\) anomalies. Darker points lying outside the shaded squares in the top left area are true anomalies but are misclassified as such. By comparing the left and right panel for each row, we could notice that KDE with distortion corrected outperforms KDE in classifying anomalies. For UMAP, almost all ground truth top \(1\%\) anomalies are not correctly identifies using KDE, while it is the other way around with the distortion corrected.

>>>>

Following similar steps to \autoref{twodgaussian}, we estimate the densities of the 4-D manifold and compare them with the ground truth density in \autoref{fig:fivedisomapden}. The bandwidth parameter for the DC-KDE estimator is set as \(r=1\) for this example. In \autoref{fig:fivedisomapden}, the log-scale ranks of the estimated density from distortion corrected KDE shown in the left panel and KDE shown in the right panel are compared with the true rank of density for four manifold learning embeddings, ISOMAP, LLE, Laplacian Eigenmaps and UMAP. Note that we exclude t-SNE algorithm in this section because it is designed mainly for low-dimensional visualization purposes and is only applicable to embedding dimensions within three.
Similar to \autoref{fig:fivedmeta}, the point shapes indicate the Gaussian mixture components and the colors indicate the distance to the kernel cores with outliers shown in darker colors. The grey shading area highlights the \(>99\%\) highest density region area and points falling into this area are the correctly classified top \(1\%\) anomalies. Darker points lying outside the shaded squares in the top left area are true anomalies but are misclassified as such. By comparing the left and right panel for each row, we could notice that KDE with distortion corrected outperforms KDE in classifying anomalies. For UMAP, almost all ground truth top \(1\%\) anomalies are not correctly identifies using KDE, while it is the other way around with the distortion corrected. It is worth noting that for DC-KDE in the left panel, there are many points having the same rank of estimated density inside the shading area, which is due to the fact that the ground truth density are almost zeros, with values less than \(10^{-7}\). And these low-density points are all captured by our distortion correction methods regardless of the dimension reduction algorithms, which again shows the robustness of DC-KDE.
